IOIs Analysis: The Sound of Teaching Music 2

### 2020-01-06 script/RNotebook/ioi_1.Rmd
remove a wrong comment
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r ioi_art_ch, echo = FALSE}
# Define phrase boundaries
df_ioi_art$Boundary <- "No"
df_ioi_art$Boundary[df_ioi_dyn$Subcomponent == "LtoS" | df_ioi_dyn$Subcomponent == "StoL" | df_ioi_dyn$Subcomponent == "FtoP" | df_ioi_art$Subcomponent == "PtoF"] <- "Yes"

@@

#### Statistics
##### Normality check
```{r normality5, echo = FALSE}
ioi_dyn_ch_norm <- by(ioi_dyn_ch$Mean, list(ioi_dyn_ch$Condition, ioi_dyn_ch$Boundary), shapiro.test)
print(ioi_dyn_ch_norm)
```
  - Violate the normality assumption

>>>>

```{r ioi_art_ch, echo = FALSE}
# Define phrase boundaries
df_ioi_art$Boundary <- "No"
df_ioi_art$Boundary[df_ioi_art$Subcomponent == "LtoS" | df_ioi_art$Subcomponent == "StoL" |
                      df_ioi_art$Subcomponent == "FtoP" | df_ioi_art$Subcomponent == "PtoF"] <- "Yes"

@@

#### Statistics
##### Normality check
```{r normality5, echo = FALSE}
ioi_dyn_ch_norm <- by(ioi_dyn_ch$Mean, list(ioi_dyn_ch$Condition, ioi_dyn_ch$Boundary), shapiro.test)
print(ioi_dyn_ch_norm)
```
